A holomorphic approach to membranes and fivebranes

### 2022-08-02 fivebranes/kr.tex
update

\section{A series of finite $N$ conjectures}

@@

In \cite{KR1}, a $\Z$-graded decomposition of $E(5|10)$ is defined which has the property that the weight zero subalgebra is isomorphic to the exceptional super Lie algebra $E(3|6)$.
We compare our decomposition of the $!$-dual factorization algebra of $\clie^\bu(\cL_{sugra})$ on the complex three-fold $Z = \C^3$, see \S \ref{s:flatdecomp}, to this decomposition considered in \cite{KR1}.
Naturally, every other graded summand appearing in the decomposition of $E(5|10)$ is a module for $E(3|6)$---it turns out that every module that appears in this way is irreducible.
Following the description of these irreducible modules given in \cite{KR1,KR2} we compute (un)refined characters and proceed to give a conjectural procedure for computing (un)refined fivebrane indices.

@@

We begin by turning to the algebraic side of things and start by recalling the weight decomposition of $E(5|10)$ constructed in \cite{KR1}.
In \S \ref{s:m5localops} we return to fivebranes and use this to give a  characterization of local operators of the twisted theory.

@@

\subsection{Irreducible representations of $E(3|6)$}
We recall the requisite knowledge of irreducible representations of $E(3|6)$ as characterized in \cite{KR1,KR2,KR3}.
The main goal of this section is to deduce explicit formulas for certain irreducible modules which we will, in turn, relate to indices of local operators of the twisted fivebrane theory.

@@

\subsection{Modified characters for degenerate modules of type $A$} \label{s:typeA}

@@

Recall that the type $A$ degenerate modules are defined by induction from the $\fg_0$-module 
\[
V = V^{\lambda_1,\lambda_3}_A \subset \C[z_i,w_a]
\] 
given by polynomials of homogenous degree $\lambda_1,\lambda_3$ in the variables $z_i,w_a$ respectively.
Thus, we have the following explicit presentation for the modified character of type $A$ modules. 
\begin{prop}
One has
\beqn\label{eqn:MA}
\ch \, \til M_A(\lambda_1,\lambda_3) = q^{y} R(t,r,t_1,t_2) \cdot \ch (V_A^{\lambda_1,\lambda_3}) (t_1^{-1},t_2^{-1},r)
\eeqn
where $y = \lambda_1 - \frac32 \lambda_3$, $R$ is as in Lemma \ref{lem:R} and 
\beqn\label{eqn:su}
\ch(V_A^{\lambda_1,\lambda_3})(t_1,t_2,r) = \ch_{SU(3)}^{\lambda_1}(t_1,t_2) \ch_{SU(2)}^{\lambda_3} (r) 
\eeqn
is the $SU(3) \times SU(2)$ character of the representation $V_A^{\lambda_1,\lambda_3}$. 
\end{prop}

@@

%which is
%\[
%0 \leftarrow I(p,0;r;\frac23 p - r) \leftarrow M(V^{p,r}) \leftarrow M(V^{p+1,r+1}) \leftarrow \cdots .
%\]
Applying the Weyl character formula we obtain the explicit expressions for the $SU(3)$ character
\begin{align*}
\ch_{SU(3)}^{\lambda_1+j} (t_1,t_2) & = t_1^{\lambda_1+j} t_2^{-\lambda_1 -j} \sum_{k=0}^{\lambda_1 + j} t_1^{-k} t_2^{2k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}} 
%\\ 
%& = t_1^{-2/3} t_2^{2/3} \sum_{k=0}^{\lambda_1 + j} t_1^{k/2} t_2^{-3k/2} \sum_{l = 0}^k (t_1 t_2)^l .
\end{align*}
and $SU(2)$ character
\begin{align*}
\ch_{SU(2)}^{\lambda_3+j} (r) & = r^{\lambda_3+j}+ r^{\lambda_3+j-2} + \cdots + r^{-\lambda_3-j} \\ & = \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} .
\end{align*}

@@

Recall that the character is given by the infinite sum
\beqn
\ch \til I_A (\lambda_1,\lambda_3) = \sum_{j \geq 0} \ch \til M_A(\lambda_1+j, \lambda_3+j)
\eeqn
For each $j \geq 0$ we have
\begin{multline}
\ch \til M_A(\lambda_1+j, \lambda_3+j) = R \cdot t^{2 \lambda_1-3 \lambda_3-j} \cdot \ch_{SU(3)}^{\lambda_1+j} \cdot \ch^{\lambda_3+j}_{SU(2)} \\ =
\frac{t^{2 \lambda_1 - 3 \lambda_3} R}{1-r^{-2}} \ch_{SU(3)}^{\lambda_1+j} t^{-j} (r^{\lambda_3 + j} - r^{-\lambda_3 - j - 2}).
\end{multline}

The first step is to deduce a closed formula for the following generating function
\beqn
\til p^{\lambda_1} (x,t_1,t_2) = \sum_{j \geq 0} \ch_{SU(3)}^{\lambda_3+j} (t_1^{-1},t_2^{-1}) x^j .
\eeqn
where we recall that $\ch_{SU(3)}^{\lambda_3+j} (t_1,t_2)$ is the $SU(3)$ character of the irreducible $SU(3)$ representation of highest weight $(\lambda_1+j,0)$.

@@

\end{lem} 
\begin{proof}
\begin{multline}
t_1^{\lambda_1} t_2^{-\lambda_1} \sum_{j \geq 0} t_1^{j} t_2^{-j} x^j \sum_{k=0}^{\lambda_1 + j}t_1^{-k} t_2^{2k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}}  \\
= \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{1-t_1^{-1} t_2^{-1}} \sum_{j \geq 0} \sum_{k=0}^{\lambda_1 + j} t_1^{j-k} t_2^{-j+2k} x^j \left(1 - t_1^{-k-1} t_2^{-k-1}\right) \\ 
= \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{1-t_1^{-1} t_2^{-1}} \sum_{j \geq 0} \left(t_1^j t_2^{-j} \frac{1-(t_1^{-1} t_2^{2})^{\lambda_1+j+1}}{1-t_1^{-1} t_2^{2}} - t_1^{j-1} t_2^{-j-1} \frac{1 - (t_1^{-2} t_2)^{\lambda_1+j+1}}{1 - t_1^{-2} t_2} \right) x^j  \\
%= \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{(1-t_1^{-1} t_2^{2})} \sum_{j \geq 0} \left( t_1^j t_2^{-j} (1-(t_1^{-1} t_2^{2})^{\lambda_1+j+1})(1 - t_1^{-2} t_2) \right. \\ \left. - t_1^{j-1} t_2^{-j-1} (1 - (t_1^{-2} t_2)^{\lambda_1+j+1})(1-t_1^{-1} t_2^{2}) \right) x^j \\ 
= F(t_1,t_2) \left( G_1 (t_1,t_2,x) - t_1^{-1} t_2^{-1} G_2 (t_1,t_2,x)\right) .
\end{multline}

Where
\begin{itemize}
\item $F(t_1,t_2) = \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{(1-t_1^{-1} t_2^{-1}) (1-t_1^{-1} t_2^{2}) (1 - t_1^{-2} t_2)}$. 
\item $G_1(t_1,t_2,x) = \frac{1}{1 - t_1^{-1} t_2^2} \sum_{j \geq 0}  t_1^j t_2^{-j} (1-(t_1^{-1} t_2^{2})^{\lambda_1+j+1}) x^j$. 
\item $G_2(t_1,t_2,x) = \frac{1}{1 - t_1^{-2} t_2}\sum_{j \geq 0} t_1^{j} t_2^{-j} (1 - (t_1^{-2} t_2)^{\lambda_1+j+1}) x^j$. 
\end{itemize}
%
%Directly, we compute
%\begin{align*}
%G_1(t_1,t_2,x) & = \frac{1}{1 - t_1 t_2^{-1} x} - \frac{t_1^{-\lambda_1-1} t_2^{2 \lambda_1 + 2}}{1 - t_2 x} \\
%G_2(t_1,t_2,x) & = \frac{1}{1-t_1 t_2^{-1} x} - \frac{t_1^{-2\lambda_1-2}t_2^{\lambda_1+1}}{1-t_1^{-1}x}
%\end{align*}
We state an intermediate lemma.
\begin{lem}
One has
\begin{align*}
G_1(t_1,t_2,x) & = \frac{1}{(1 - t_1 t_2^{-1} x)(1-t_2 x)} \big(1 + h(t_1,t_2,x) \big) \\
G_2(t_1,t_2,x) & = \frac{1}{(1 - t_1 t_2^{-1} x)(1-t_1^{-1} x)} \left(1 + t_1^{-1} t_2^{-1} h(t_1,t_2,x) \right) .
\end{align*}
where $h_{\lambda_1}(t_1,t_2,x)$ is as in equation \eqref{eqn:h}. 
\end{lem}

@@

%\begin{multline}
%t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1} \sum_{j \geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) R \sum_{k=0}^{\lambda_1 + j}t_1^{2k} t_2^{-k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}}  \\
%= \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{1-t_1^{-1} t_2^{-1}} R \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \sum_{k=0}^{\lambda_1 + j} t_1^{2k} t_2^{-k} \left(1 - (t_1t_2)^{-k-1}\right) \\
%= \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{1-t_1^{-1} t_2^{-1}} R \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \left(\frac{1 - (t_1^2 t_2^{-1})^{\lambda_1 + j + 1}}{1 - t_1^2 t_2^{-1}} - t_1^{-1} t_2^{-1} \frac{1 - (t_1 t_2^{-2})^{\lambda_1 + j + 1}}{1 - t_1 t_2^{-2}} \right) \\ =
%\frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{(1-t_1^{-1} t_2^{-1})(1 - t_1^2 t_2^{-1})(1-t_1t_2^{-1})} R \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \times \\ 
%\left[(1-t_1 t_2^{-2})(1-(t_1^2 t_2^{-1})^{\lambda_1+j+1}) - t_1^{-1}t_2^{-1} (1-t_1^2 t_2^{-1}) (1 - (t_1 t_2^{-2})^{\lambda_1+j+1}) \right]
%%
%%\\ = \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{(1-t_1^{-1} t_2^{-1})(1 - t_1^2 t_2^{-1})(1-t_1t_2^{-1})} \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \\ \times \left(1 + t_1^{2\lambda_1 +2j+3}t_2^{-\lambda_1-j-1} - t_1 t_2^{-2} - t_1^{2 \lambda_1 + 2j + 2} t_2^{-\lambda_1 - j -1} \right. \\ \left. - t_1^{-1} t_2^{-1} + t_1^{\lambda_1+j+2} t_2^{-2 \lambda_1 - 2j-4} + t_1 t_2^{-2} + t_1^{\lambda_1 + j} t_2^{-2\lambda_1 - 2 j - 3} \right)
%\end{multline}
%
%We split the sum $\sum_{j \geq 0}$ into four terms
%\begin{itemize}
%\item the first term is 
%\beqn
%(1-t_1t_2^{-2}) \sum_{j \geq 0} t^j r^{\lambda_3 + j} \left(t_1^{-j} t_2^j - t_1^{2 \lambda_1 + j + 2} t_2^{-\lambda_1 - 1} \right) .
%\eeqn
%Evaluating the infinite series this becomes
%\begin{multline} 
%r^{\lambda_3} (1-t_1 t_2^{-2}) \left(\frac1{1-trt_1^{-1}t_2} - \frac{t_1^{2\lambda_1+2}t_2^{-\lambda_1-1}}{1 - t r t_1} \right) \\ = \frac{r^{\lambda_3}(1-t_1 t_2^{-2})}{(1-trt_1^{-1}t_2)(1 - t r t_1)} \left(1 - trt_1-t_1^{2\lambda_1+2} t_2^{-\lambda_1-1}+tr t_1^{2 \lambda_1+1} t_2^{-\lambda_2}\right)
%\end{multline}
%\item the second term is
%\beqn
%t_1^{-1} t_2^{-1}(1-t_1^2 t_2^{-1}) \sum_{j \geq 0} t^j r^{\lambda_3 + j} \left(t_1^{-j} t_2^j - t_1^{\lambda_1+1} t_2^{-2\lambda_1 - j - 2}\right) .
%\eeqn
%\end{itemize}
\subsection{Characters for degenerate modules of type B} \label{s:typeB}

@@

\begin{prop}
\label{prop:chB}
For $\lambda_3 \geq 0$ the character $\ch \til I_B(0,\lambda_3)$ specialized at $t_1=t_2=1$ is given by the expression
\begin{multline}
\label{eqn:chB3}
t^{2 \lambda_3 + 6} R(t,r) \frac{1-t^{\lambda_3+1}}{1 - t} \\ + \frac{t^{2\lambda_3 + 10}}{(1-t^2)^3 (1-r^{-2})} \left(p_{\lambda_3+2} (t^{-1} r) (1 - t^{-1} r^{-1})^3 - r^{-2} p_{\lambda_3}(t^{-1} r^{-1})(1-t^{-1}r)^3 \right) 
\end{multline}
where the polynomial $p_{\lambda_3 + 2}(x)$ is as in Proposition \ref{prop:chB}. 
\end{prop}

\begin{proof}
We have already computed $\ch\til I_A(\lambda_1,\lambda_3)$ for any pair $(\lambda_1,\lambda_3)$ in \S \ref{s:typA}.
Thus, it suffices to compute the modified character of the type $B$ Verma modules 
\[
\til M_{B}(k,\lambda_3-k) .
\]

The character of the Verma module $\til M_B(k,\lambda_3-k)$, for $0 \leq k \leq \lambda_3$, is given by
\[
\ch \til M_B(k,\lambda_3-k)|_{t_1=t_2=1} = t^{3 \lambda_3 - k + 6} R(t,r) .
\]
Thus, \eqref{eqn:chB2} simplifies to 
\[
\ch \til I_B(0,\lambda_3) = t^{2 \lambda_3 + 6} R(t,r) \frac{1-t^{\lambda_3+1}}{1 - t} + \ch \til I_{A}(\lambda_3+2,0) .
\]
The result now follows from the formula for $\ch \til I_A(\lambda_3+2,0)$ given in Proposition~\ref{prop:chA}.
\end{proof}

@@

>>>>

\section{A series of finite $N$ conjectures}
\label{s:kr}

@@

In \cite{KR2}, a $\Z$-graded decomposition of $E(5|10)$ is defined which has the property that the weight zero subalgebra is isomorphic to the exceptional super Lie algebra $E(3|6)$.
We compare our decomposition of the $!$-dual factorization algebra of $\clie^\bu(\cL_{sugra})$ on the complex three-fold $Z = \C^3$, see \S \ref{s:flatdecomp}, to this decomposition considered in \cite{KR2}.
Naturally, every other graded summand appearing in the decomposition of $E(5|10)$ is a module for $E(3|6)$---it turns out that every module that appears in this way is irreducible.
Following the description of these irreducible modules constructed in \cite{KR1,KR2} we compute (un)refined characters and proceed to give a conjectural procedure for computing (un)refined fivebrane indices.

@@

We begin by turning to the algebraic side of things and start by recalling the weight decomposition of $E(5|10)$ constructed in \cite{KR2}.
In \S \ref{s:m5localops} we return to fivebranes and use this to give a  characterization of local operators of the twisted theory.

@@

\subsection{Irreducible representations of $E(3|6)$}
We recall the requisite knowledge of irreducible representations of $E(3|6)$ as characterized in~\cite{KR1,KR2,KR3}.
The main goal of this section is to deduce explicit formulas for certain irreducible modules which we will, in turn, relate to indices of local operators of the twisted fivebrane theory.

@@

\subsection{Character of modified type $A$ modules} \label{s:typeA}

@@

Recall that the type $A$ degenerate modules are defined by induction from the $\fg_0$-module 
\[
V = V^{\lambda_1,\lambda_3}_A \subset \C[z_i,w_a]
\] 
given by polynomials of homogenous degree $\lambda_1,\lambda_3$ in the variables $z_i,w_a$ respectively.
Thus, we have the following explicit presentation for the modified character of type $A$ modules. 
\begin{prop}
One has
\beqn\label{eqn:MA}
\ch \, \til M_A(\lambda_1,\lambda_3) = t^{y_A} R(t,r,t_1,t_2) \cdot \ch (V_A^{\lambda_1,\lambda_3}) (t_1^{-1},t_2^{-1},r)
\eeqn
where $y_A = 2\lambda_1 - 3 \lambda_3$, $R$ is as in Lemma \ref{lem:R} and 
\beqn\label{eqn:su}
\ch(V_A^{\lambda_1,\lambda_3})(t_1,t_2,r) = \ch_{SU(3)}^{\lambda_1}(t_1,t_2) \ch_{SU(2)}^{\lambda_3} (r) 
\eeqn
is the $SU(3) \times SU(2)$ character of the representation $V_A^{\lambda_1,\lambda_3}$. 
\end{prop}

@@

%which is
%\[
%0 \leftarrow I(p,0;r;\frac23 p - r) \leftarrow M(V^{p,r}) \leftarrow M(V^{p+1,r+1}) \leftarrow \cdots .
%\]
Applying the Weyl character formula we obtain the explicit expressions for the $SU(3)$ character
\begin{align*}
\ch_{SU(3)}^{\lambda_1+j} (t_1^{-1},t_2^{-1}) & = t_1^{\lambda_1+j} t_2^{-\lambda_1 -j} \sum_{k=0}^{\lambda_1 + j} t_1^{-k} t_2^{2k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}} 
%\\ 
%& = t_1^{-2/3} t_2^{2/3} \sum_{k=0}^{\lambda_1 + j} t_1^{k/2} t_2^{-3k/2} \sum_{l = 0}^k (t_1 t_2)^l .
\end{align*}
and $SU(2)$ character
\begin{align*}
\ch_{SU(2)}^{\lambda_3+j} (r) & = r^{\lambda_3+j}+ r^{\lambda_3+j-2} + \cdots + r^{-\lambda_3-j} \\ & = \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} .
\end{align*}

@@

Recall that the character is given by the infinite sum
\beqn
\ch \til I_A (\lambda_1,\lambda_3) = \sum_{j \geq 0} \ch \til M_A(\lambda_1+j, \lambda_3+j)
\eeqn
For each $j \geq 0$ we have
\begin{multline}
\ch \til M_A(\lambda_1+j, \lambda_3+j) = R \cdot t^{2 \lambda_1-3 \lambda_3-j} \cdot \ch_{SU(3)}^{\lambda_1+j}(t_1^{-1},t_2^{-1}) \cdot \ch^{\lambda_3+j}_{SU(2)}(r) \\ =
\frac{t^{2 \lambda_1 - 3 \lambda_3} R}{1-r^{-2}} \ch_{SU(3)}^{\lambda_1+j} (t_1^{-1},t_2^{-1}) t^{-j} (r^{\lambda_3 + j} - r^{-\lambda_3 - j - 2}).
\end{multline}

The first step is to deduce a closed formula for the following generating function
\beqn
\til p^{\lambda_1} (x,t_1,t_2) = \sum_{j \geq 0} \ch_{SU(3)}^{\lambda_1+j} (t_1^{-1},t_2^{-1}) x^j .
\eeqn
where we recall that $\ch_{SU(3)}^{\lambda_3+j} (t_1,t_2)$ is the $SU(3)$ character of the irreducible $SU(3)$ representation of highest weight $(\lambda_1+j,0)$.

@@

\end{lem} 
\begin{proof}
We start by expanding the expression for the generating function $\til p_{\lambda_1}(t_1,t_2,x)$:
\begin{multline}
t_1^{\lambda_1} t_2^{-\lambda_1} \sum_{j \geq 0} t_1^{j} t_2^{-j} x^j \sum_{k=0}^{\lambda_1 + j}t_1^{-k} t_2^{2k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}}  \\
= \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{1-t_1^{-1} t_2^{-1}} \sum_{j \geq 0} \sum_{k=0}^{\lambda_1 + j} t_1^{j-k} t_2^{-j+2k} x^j \left(1 - t_1^{-k-1} t_2^{-k-1}\right) \\ 
= \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{1-t_1^{-1} t_2^{-1}} \sum_{j \geq 0} \left(t_1^j t_2^{-j} \frac{1-(t_1^{-1} t_2^{2})^{\lambda_1+j+1}}{1-t_1^{-1} t_2^{2}} - t_1^{j-1} t_2^{-j-1} \frac{1 - (t_1^{-2} t_2)^{\lambda_1+j+1}}{1 - t_1^{-2} t_2} \right) x^j  \\
%= \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{(1-t_1^{-1} t_2^{2})} \sum_{j \geq 0} \left( t_1^j t_2^{-j} (1-(t_1^{-1} t_2^{2})^{\lambda_1+j+1})(1 - t_1^{-2} t_2) \right. \\ \left. - t_1^{j-1} t_2^{-j-1} (1 - (t_1^{-2} t_2)^{\lambda_1+j+1})(1-t_1^{-1} t_2^{2}) \right) x^j \\ 
= F(t_1,t_2) \left( G_1 (t_1,t_2,x) - t_1^{-1} t_2^{-1} G_2 (t_1,t_2,x)\right) .
\end{multline}

Here, we have introduced the following functions
\begin{itemize}
\item $F(t_1,t_2) = \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{(1-t_1^{-1} t_2^{-1}) (1-t_1^{-1} t_2^{2}) (1 - t_1^{-2} t_2)}$. 
\item $G_1(t_1,t_2,x) = \frac{1}{1 - t_1^{-1} t_2^2} \sum_{j \geq 0}  t_1^j t_2^{-j} (1-(t_1^{-1} t_2^{2})^{\lambda_1+j+1}) x^j$. 
\item $G_2(t_1,t_2,x) = \frac{1}{1 - t_1^{-2} t_2}\sum_{j \geq 0} t_1^{j} t_2^{-j} (1 - (t_1^{-2} t_2)^{\lambda_1+j+1}) x^j$. 
\end{itemize}
%
%Directly, we compute
%\begin{align*}
%G_1(t_1,t_2,x) & = \frac{1}{1 - t_1 t_2^{-1} x} - \frac{t_1^{-\lambda_1-1} t_2^{2 \lambda_1 + 2}}{1 - t_2 x} \\
%G_2(t_1,t_2,x) & = \frac{1}{1-t_1 t_2^{-1} x} - \frac{t_1^{-2\lambda_1-2}t_2^{\lambda_1+1}}{1-t_1^{-1}x}
%\end{align*}
We state an intermediate lemma.
\begin{lem}
One has
\begin{align*}
G_1(t_1,t_2,x) & = \frac{1}{(1 - t_1 t_2^{-1} x)(1-t_2 x)} \big(1 + h(t_1,t_2,x) \big) \\
G_2(t_1,t_2,x) & = \frac{1}{(1 - t_1 t_2^{-1} x)(1-t_1^{-1} x)} \left(1 + t_1^{-1} t_2^{-1} h(t_1,t_2,x) \right) .
\end{align*}
where $h_{\lambda_1}(t_1,t_2,x)$ is as in equation \eqref{eqn:h1}. 
\end{lem}

@@

%\begin{multline}
%t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1} \sum_{j \geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) R \sum_{k=0}^{\lambda_1 + j}t_1^{2k} t_2^{-k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}}  \\
%= \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{1-t_1^{-1} t_2^{-1}} R \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \sum_{k=0}^{\lambda_1 + j} t_1^{2k} t_2^{-k} \left(1 - (t_1t_2)^{-k-1}\right) \\
%= \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{1-t_1^{-1} t_2^{-1}} R \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \left(\frac{1 - (t_1^2 t_2^{-1})^{\lambda_1 + j + 1}}{1 - t_1^2 t_2^{-1}} - t_1^{-1} t_2^{-1} \frac{1 - (t_1 t_2^{-2})^{\lambda_1 + j + 1}}{1 - t_1 t_2^{-2}} \right) \\ =
%\frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{(1-t_1^{-1} t_2^{-1})(1 - t_1^2 t_2^{-1})(1-t_1t_2^{-1})} R \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \times \\ 
%\left[(1-t_1 t_2^{-2})(1-(t_1^2 t_2^{-1})^{\lambda_1+j+1}) - t_1^{-1}t_2^{-1} (1-t_1^2 t_2^{-1}) (1 - (t_1 t_2^{-2})^{\lambda_1+j+1}) \right]
%%
%%\\ = \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{(1-t_1^{-1} t_2^{-1})(1 - t_1^2 t_2^{-1})(1-t_1t_2^{-1})} \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \\ \times \left(1 + t_1^{2\lambda_1 +2j+3}t_2^{-\lambda_1-j-1} - t_1 t_2^{-2} - t_1^{2 \lambda_1 + 2j + 2} t_2^{-\lambda_1 - j -1} \right. \\ \left. - t_1^{-1} t_2^{-1} + t_1^{\lambda_1+j+2} t_2^{-2 \lambda_1 - 2j-4} + t_1 t_2^{-2} + t_1^{\lambda_1 + j} t_2^{-2\lambda_1 - 2 j - 3} \right)
%\end{multline}
%
%We split the sum $\sum_{j \geq 0}$ into four terms
%\begin{itemize}
%\item the first term is 
%\beqn
%(1-t_1t_2^{-2}) \sum_{j \geq 0} t^j r^{\lambda_3 + j} \left(t_1^{-j} t_2^j - t_1^{2 \lambda_1 + j + 2} t_2^{-\lambda_1 - 1} \right) .
%\eeqn
%Evaluating the infinite series this becomes
%\begin{multline} 
%r^{\lambda_3} (1-t_1 t_2^{-2}) \left(\frac1{1-trt_1^{-1}t_2} - \frac{t_1^{2\lambda_1+2}t_2^{-\lambda_1-1}}{1 - t r t_1} \right) \\ = \frac{r^{\lambda_3}(1-t_1 t_2^{-2})}{(1-trt_1^{-1}t_2)(1 - t r t_1)} \left(1 - trt_1-t_1^{2\lambda_1+2} t_2^{-\lambda_1-1}+tr t_1^{2 \lambda_1+1} t_2^{-\lambda_2}\right)
%\end{multline}
%\item the second term is
%\beqn
%t_1^{-1} t_2^{-1}(1-t_1^2 t_2^{-1}) \sum_{j \geq 0} t^j r^{\lambda_3 + j} \left(t_1^{-j} t_2^j - t_1^{\lambda_1+1} t_2^{-2\lambda_1 - j - 2}\right) .
%\eeqn
%\end{itemize}

\subsection{Character of modified type $B$ modules} \label{s:typeB}

@@

Recall that the type $B$ degenerate modules are defined by induction from the $\fg_0$-module 
\[
V = V^{\lambda_1,\lambda_3}_B \subset \C[z_i,\del_{w_a}]
\] 
given by polynomials of homogenous degree $\lambda_1,\lambda_3$ in the variables $z_i,\del_{w_a}$ respectively.
As in the type $A$ case, we have the following expression for the character of the modified type $B$ module.

%\begin{prop}
%One has
%\beqn\label{eqn:MA}
%\ch \, \til M_B(\lambda_1,\lambda_3) = t^{y_B} R(t,r,t_1,t_2) \cdot \ch (V_B^{\lambda_1,\lambda_3}) (t_1^{-1},t_2^{-1},r)
%\eeqn
%where $y_B = 2\lambda_1 + 3 \lambda_3+6$, $R$ is as in Lemma \ref{lem:R} and
%\beqn\label{eqn:suB}
%\ch(V_B^{\lambda_1,\lambda_3})(t_1,t_2,r) = \ch_{SU(3)}^{\lambda_1}(t_1,t_2) \ch_{SU(2)}^{\lambda_3} (r) 
%\eeqn
%is the $SU(3) \times SU(2)$ character of the representation $V_B^{\lambda_1,\lambda_3}$.
%\end{prop}

Just as in the type A case we can compute the character of the Verma module $\til M_B(l,\lambda_3-l)$, for $0 \leq l \leq \lambda_3$ by the formula
\beqn\label{eqn:chMB}
\ch \til M_B(l,\lambda_3-l) = t^{3 \lambda_3 - l + 6} R(t,t_1,t_2,r) \ch_{SU(3)}^{l}(t_1^{-1},t_2^{-1}) \ch_{SU(2)}^{\lambda_3-l} (r)  .
\eeqn
Introduce the generating function
\beqn
\til q_{\lambda_3} (t_1,t_2,x) = \sum_{l=0}^{\lambda_3} \ch^l_{SU(3)} (t_1^{-1},t_2^{-1}) x^l 
\eeqn

%\begin{prop}
%\label{prop:chB}
%For $\lambda_3 \geq 0$ the character $\ch \til I_B(0,\lambda_3)$ specialized at $t_1=t_2=1$ is given by the expression
%\begin{multline}
%\label{eqn:chB3}
%t^{2 \lambda_3 + 6} R(t,r) \frac{1-t^{\lambda_3+1}}{1 - t} \\ + \frac{t^{2\lambda_3 + 10}}{(1-t^2)^3 (1-r^{-2})} \left(p_{\lambda_3+2} (t^{-1} r) (1 - t^{-1} r^{-1})^3 - r^{-2} p_{\lambda_3}(t^{-1} r^{-1})(1-t^{-1}r)^3 \right) 
%\end{multline}
%where the polynomial $p_{\lambda_3 + 2}(x)$ is as in Proposition \ref{prop:chB}. 
%\end{prop}

\begin{thm}
\label{thm:chB}
For $\lambda_3 \geq 0$ the character $\ch \til I_B(0,\lambda_3)$ is given by the expression
\begin{multline}
\label{eqn:chB3}
\frac{t^{2 \lambda_3 + 6} R(t,t_1,t_2,r)}{1-r^{-2}} \left(r^{\lambda_3} \til q_{\lambda_3} (t_1,t_2,t^{-1}r^{-1}) - r^{-\lambda_3-2} \til q_{\lambda_3} (t_1,t_2,t^{-1}r) \right) \\ + \frac{t^{2 \lambda_3+10}}{(1-t_1^{-1} t^2)(1-t_1t_2^{-1}t^2)(1-t_2 t^2)(1-r^{-2})} \times \\
\left(p_{\lambda_3+2}(t_1,t_2,t^{-1} r) (1-t_1^{-1} r^{-1} t^{-1})(1-t_1t_2^{-1} r^{-1} t^{-1})(1-t_2 r^{-1} t^{-1}) \right.
\\
- \left. r^{-2} p_{\lambda_3+2}(t_1,t_2,r^{-1} t^{-1})(1-t_1^{-1} r t^{-1})(1-t_1t_2^{-1} r t^{-1})(1-t_2 r t^{-1}) \right)
\end{multline}
where the polynomial $p_{\lambda_3 + 2}(x)$ is as in Theorem \ref{thm:refinedA}.
\end{thm}

\begin{proof}
We have already computed $\ch\til I_A(\lambda_1,\lambda_3)$ for any pair $(\lambda_1,\lambda_3)$ in Theorem~\ref{thm:refinedA}.
The formula for $\ch \til I_A(\lambda_3+2,0)$ accounts for the last two lines in the stated formula.

It suffices to compute the character of the modified type $B$ Verma modules 
\[
\til M_{B}(k,\lambda_3-k) .
\]

%Thus, \eqref{eqn:chB2} simplifies to 
%\[
%\ch \til I_B(0,\lambda_3) = t^{2 \lambda_3 + 6} R(t,r) \frac{1-t^{\lambda_3+1}}{1 - t} + \ch \til I_{A}(\lambda_3+2,0) .
%\]
%The result now follows from the formula for $\ch \til I_A(\lambda_3+2,0)$ given in Proposition~\ref{prop:chA}.
\end{proof}

@@

\parsec[s:firstcase]

Let's unpack the character of the simplest module of type $B$, namely $\til I_B(0,0)$.
